Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-05-28 fmics/paper.tex
fix typo

Under such a constraint, we have proved the follwoing result bounding the error of $\mathsf{output}\;D\;n\;x\;t$ compared to $\mathsf{exact}\;D\;n\;x\;t$.
\begin{theorem}\label{max_error}
For all $k$ and $D$ satisfying $|D\;(t'+1)-D\;t'|\leq k$ at all times, the following holds for all slices $n>0$, tap positions $x$, and times $t$:
\begin{multline*}
t>(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay}\;n)+\mathsf{delay}\;n+\mathsf{delay\_sum}\;n\implies\\
|\mathsf{output}\;D\;n\;x\;t-\mathsf{exact}\;D\;n\;x\;t|\leq(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay\;n})\times k\times\\
(\mathsf{delay\_sum}\;n-1+t\operatorname{mod}\mathsf{delay}\;n)
\end{multline*}
Furthermore, for all $k$ there exists an input stream $D_k$ satisfying $|D_k\;(t'+1)-D_k\;t'|\leq k$ for all $t'$ and 
\begin{multline*}
|\mathsf{output}\;D_k\;n\;x\;t-\mathsf{exact}\;D_k\;n\;x\;t|=(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay\;n})\times k\times\\
(\mathsf{delay\_sum}\;n-1+t\operatorname{mod}\mathsf{delay}\;n)
\end{multline*}

>>>>

Under such a constraint, we have proved the following result bounding the error of $\mathsf{output}\;D\;n\;x\;t$ compared to $\mathsf{exact}\;D\;n\;x\;t$.
\begin{theorem}\label{max_error}
For all $k$ and $D$ satisfying $|D\;(t'+1)-D\;t'|\leq k$ at all times, the following holds for all slices $n>0$, tap positions $x$, and times $t$:
\begin{multline*}
t>(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay}\;n)+\mathsf{delay}\;n+\mathsf{delay\_sum}\;n\implies\\
|\mathsf{output}\;D\;n\;x\;t-\mathsf{exact}\;D\;n\;x\;t|\leq(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay\;n})\times k\times\\
(\mathsf{delay\_sum}\;n-1+t\operatorname{mod}\mathsf{delay}\;n)
\end{multline*}
Furthermore, for all $k$ there exists an input stream $D_k$ satisfying $|D_k\;(t'+1)-D_k\;t'|\leq k$ for all $t'$ and 
\begin{multline*}
|\mathsf{output}\;D_k\;n\;x\;t-\mathsf{exact}\;D_k\;n\;x\;t|=(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay\;n})\times k\times\\
(\mathsf{delay\_sum}\;n-1+t\operatorname{mod}\mathsf{delay}\;n)
\end{multline*}
